### 2023-09-12 main.tex
lkj

Multiplying by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is

@@

	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu-\xi_{k}^{1}+\xi_{k}^{1}-r_{a}+r_{a}}\\=&
	\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
Multiplying by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is

@@

Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 

@@

The aim of this section is to give an answer to these questions. We first define a more general process with arbitrary number of species and arbitrary occupation on a general finite graph, checking that in the case of a chain we obtain average occupation evolution equations with N discrete Laplacians and a reaction term. Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case. 

@@

Considering again a finite and connected graph $G=(V,\mathcal{E})$ with set of vertices $V$ and set of edges $\mathcal{E}$, we introduce the generator

@@

	\mathcal{L}^{rd}=\sum_{x,y\in\mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\mathcal{L}_{x}^{rd}

@@

	\mathcal{L}_{x,y}^{rd}=\sigma_{11}\mathcal{L}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,y}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,y}^{m}
with $\mathcal{L}_{x,y}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
	\mathcal{L}_{x,y}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-f(\bm{n})\right)

@@

		k+c \quad &\text{if}\quad k+c\leq N\\
		k+c-N+1\quad &\text{if}\quad k+c>N\\
		1\quad &\text{if}\quad k=1

@@

	\mathcal{L}_{x,y}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)

@@

	\mathcal{L}_{x}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)

@@

		\alpha_{a}^{x}&=\sigma_{11}\rho_{a}^{x}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
		\alpha_{1}^{x}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=2}^{N}\alpha_{a}^{x}

@@

\textbf{Remark}: observe that the site generator $\mathcal{L}_{x}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}. We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}^{x}$, as specified above. 

@@

For arbitrary edge $(x,y)\in \mathcal{E}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{2,\ldots,N\}$ at site $x\in V $ of the edge generator $\mathcal{L}_{x,y}^{rd}$ reads

@@

		\mathcal{L}_{x,y}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{y}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{y}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})

@@

	\mathcal{L}_{x,y}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\nu\left(n_{d}^{y}-n_{d}^{x}\right)

@@

		\mathcal{L}_{x,y}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{y}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{y}-\bm{\delta}_{b}^{y})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{y}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{y}
		\sum_{a=2}^{N}n_{a}^{x}n_{q}^{y}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{y}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{y}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{y}\right)
		\nu(n_{q}^{y}-n_{d}^{x})

@@

\paragraph{Action on the occupation variable of $\mathcal{L}_{x}^{rd}$}
Acting on $n_{d}^{x}$  with $\mathcal{L}_{x}^{rd}$ we obtain

@@

		\mathcal{L}_{x}^{rd}n_{d}^{x}&=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left((n_{d}^{x}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-n_{d}^{x}\right)=\alpha_{d}^{x}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{x}-n_{d}^{x}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}^{x}
		\alpha_{d}^{x}\left(\nu-n_{d}^{x}\right)-n_{d}^{x}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}^{x}\right)
		\\&=\alpha_{d}^{x}\nu-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
		\nu\sigma_{11}\rho_{d}^{x}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{x}\right)-n_{d}^{x}\nu(\sigma_{11}+(N-2)\sigma_{12})
\subsection{The process on a chain}
Here we consider the geometry of a chain of length $L$ with two reservoirs connected with the end sites $1$ and $L$. This geometry is the same used in section \ref{sectionIntegrabiliy}, but now the occupation variable is arbitrary and denoted by $\nu\in \mathbb{N}$.\\

@@

\subsection{Reversible measure} 

@@

	\Lambda_{rev}=\bigtimes_{x\in V}\Lambda_{rev}^{x}

@@

	\alpha_{a}^{x}=\alpha_{a}\quad \forall x\in V\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{2,\ldots,N\}

@@

	\rho=\rho_{a}=\frac{\alpha}{\alpha_{1}+(N-1)\alpha}\quad \forall a\in \{2,\ldots,N\}\qquad \text{and}\qquad \rho_{1}=\frac{\alpha_{1}}{\alpha_{1}+(N-1)\alpha}

@@

	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho_{1}^{n_{1}^{x}}\rho^{\sum_{a=2}^{N}n_{a}^{x}}
This can be proved just by imposing the detailed balance conditions for the edge and for the site generators. For fixed edge $(x,y)\in \mathcal{E}$ and $x\in V$ the detailled balances for $\mathcal{L}_{x,y}$ and for $\mathcal{L}_{x}$ are analogous, while for $\mathcal{L}_{x,y}^{c}$ with $c\in\{1,\ldots,N-2\}$ we have the following. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{y}-\delta_{b}^{y}$; the detailled balance reads
		&n_{a}^{x}n_{b}^{y}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots n_{b}^{y}!\cdots n_{g_{c}(a)}^{y}!\ldots n_{N}^{y}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{y}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{y}}

@@

		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{y}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{y}!\cdots (n_{b}^{y}-1)!\cdots (n_{g_{c}(a)}^{y}+1)!\ldots n_{N}^{y}!}

@@

		\rho_{1}^{n_{1}^{x}+n_{1}^{y}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{y}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{y}}

@@

By similar computation it is possible to show that the same claim is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$, related to the generator $\mathcal{L}^{m}_{x,y}$. \\
For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\alpha_{a}^{x}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{|\alpha|}$. As a consequence we have the result. 
\subsection{Duality}

@@

	\widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N-1})
To each site $x\in V$ we associate an ``extra site'', denoted $u(x)$,

@@

	\bm{\xi}=\left(\xi_{1}^{x},\ldots,\xi_{N}^{x},\xi_{2}^{u(x)},\ldots,\xi_{N}^{u(x)}\right)_{x\in V}

@@

and the component $\xi_{a}^{u(x)}$  gives the number of dual particles of type $a\in \{2,\ldots,N\}$ at 

@@

	D(\bm{n},\bm{\xi})=\prod_{x\in V}\left(\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}\,\right)

@@

	\widetilde{\mathcal{L}}^{rd}=\sum_{(x,y)\in \mathcal{E}}\omega_{x,y}\mathcal{L}_{x,y}^{rd}+\sum_{x\in V}\Gamma_{x}\widetilde{\mathcal{L}}_{x}^{rd}

@@

$\mathcal{L}_{x,y}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{x}^{rd}$ is again the absorbing dual generator $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator}. 

@@

	H^{rd}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\left(\sigma_{11}\mathcal{H}_{x,y}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,y}^{m}\right)+\sum_{x\in V}\Gamma_{x}H_{x}
where $\mathcal{H}_{x,y}$ and $H_{x}$ are \eqref{edgeHamiltonian} and \eqref{siteHamiltonian} respectively, 
	\mathcal{H}_{x,y}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}^{c}\otimes E_{g_{c}(b)a}^{y}-E_{aa}^{x}\otimes E_{bb}^{y}\right)

@@

	\mathcal{H}_{x,y}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}^{x}\otimes \mathbbm{1}^{y}-E_{aa}^{x}\otimes \mathbbm{1}^{y}\right)
Similarly, we will define the dual Hamiltonian $\widetilde{H}^{rd}$. For the edge dynamics, the original and the dual Hamiltonians do coincide, while the site one it is again $\widetilde{H}_{x}$ defined in \eqref{siteDualHamiltonian}, but with the parameters introduced in \eqref{boundaryParamRD}.\\ We aim to show

@@

Therefore, we need to prove that
	(\mathcal{H}_{x,y}^{rd})^{T}D&=D\mathcal{H}_{x,y}^{rd}\label{edgeDualityRelationRD}\\
	H_{x}^{T}D&=D\widetilde{H}_{x}D\label{siteDualityRelationRD}
where the duality matrix $D$ is again \eqref{dualityMatrix}. As already pointed out, $H_{x}$ and $\widetilde{H}_{x}$ have the same structure (up to a specific choice of the reservoirs parameters), while $\mathcal{H}_{x,y}^{rd}$ has two more terms $\sum_{c=1}^{N-2}\mathcal{H}_{x,y}^{c}$ and $\mathcal{H}_{x,y}^{m}$. Therefore, we only need to show that 
	&(\mathcal{H}_{x,y}^{c})^{T}D=D\mathcal{H}_{x,y}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
	&(\mathcal{H}_{x,y}^{m})^{T}D=D\mathcal{H}_{x,y}^{m}\label{mDualityRelation}

>>>>

We consider the first addend in the curly bracket of the previous equation. We multiplying it by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$ and by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}$ and we have

@@

	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}\nonumber\\=&
	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{1}^{k}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
	\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\nonumber
	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{1}^{k}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}
where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets.
We multiplying it by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ 

@@

where we used again the multinomial theorem. Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 

@@

The aim of this section is to give an answer to these questions. We first define the process on a chain in order to obtain average occupation evolution equations with $N-1$ discrete Laplacians and a reaction term. Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case. 

@@

We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{a})_{a\in\{1,\ldots,N\}}$ is attached at left of site $1$ and a reservoir with parameters $(\beta_{a})_{a\in\{1,\ldots,N\}}$ is attached at right of site $L$. The generator reads

@@

	\mathcal{L}^{rd}=+\mathcal{L}_{right}^{rd}\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\mathcal{L}_{right}^{rd}

@@

	\mathcal{L}_{x,x+1}^{rd}=\sigma_{11}\mathcal{L}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{L}_{x,x+1}^{c}+(\Upsilon-2\nu\sigma_{12})\mathcal{L}_{x,x+1}^{m}
with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$
	\mathcal{L}_{x,x+1}^{c}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-f(\bm{n})\right)

@@

		k+c \quad &\text{if}\quad k+c< N \\
		k+c-N+1\quad &\text{if}\quad k+c\geq N,\quad k\neq N\\
		1\quad &\text{if}\quad k=N

@@

	\mathcal{L}_{x,x+1}^{m}f(\bm{n})=\sum_{a,b=1}^{N}n_{a}^{x}\left(f(\bm{n}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x})-f(\bm{n})\right)

@@

	\mathcal{L}_{left}^{rd}f(\bm{n})=\sum_{a,b=1}^{N}\alpha_{a}^{x}n_{b}^{x}\left(f(\bm{n}-\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x})-f(\bm{n})\right)

@@

		\alpha_{a}&=\sigma_{11}\rho_{a}^{L}+\sigma_{12}\sum_{b=2\,:\,b\neq a}^{N}\rho_{b}^{x}\qquad \text{if} \quad k\in \{2,\ldots,N\}\\
		\alpha_{N}&=\nu\left(\sigma_{11}+(N-2)\sigma_{12}\right)-\sum_{a=1}^{N-1}\alpha_{a}

@@

The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analugosly, but the $\alpha$'s are replaced by $\beta$'s. \\ \\
\textbf{Remark}: observe that the site generator $\mathcal{L}_{left}^{rd}$ has the form of the one of the multi-species stirring process \eqref{siteGenerator}. We wrote it with the uppercase 'rd' in order to underline the fact that we need a specific choice of the reservoirs parameters $\alpha_{a}$, as specified above. 

@@

For arbitrary site $x\in \{1,\ldots,L\}$, the action on the occupation variable $f(\bm{n})=n_{d}^{x}$ of particle of type $d\in \{1,\ldots,N-1\}$ reads

@@

		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{q=2\,:	,q\neq d}^{N}(n_{c}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=2}^{N}(n_{b}^{x}-n_{\alpha}^{x})

@@

	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{b}^{x}+\bm{\delta}_{a}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\nu\left(n_{d}^{x+1}-n_{d}^{x}\right)

@@

		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{a,b=1}^{N}n_{a}^{x}n_{b}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{a}^{x}+\bm{\delta}_{g_{c}(b)}^{x}+\bm{\delta}_{g_{c}(a)}^{x+1}-\bm{\delta}_{b}^{x+1})-n_{d}^{x}\right)=\sum_{a=1}^{N}n_{a}^{x}n_{q}^{x+1}-\sum_{\ell=1}^{N}n_{d}^{x}n_{\ell}^{x+1}
		\sum_{a=2}^{N}n_{a}^{x}n_{q}^{x+1}-\left(\nu-\sum_{i=2}^{N}n_{i}^{x}\right)n_{q}^{x+1}-\sum_{\ell=2}^{N}n_{d}^{x}n_{\ell}^{x+1}-n_{d}^{x}\left(\nu-\sum_{i=2}^{N}n_{i}^{x+1}\right)
		\nu(n_{q}^{x+1}-n_{d}^{x})

@@

\paragraph{Action on the occupation variable of $\mathcal{L}_{left}^{rd}$}
Acting on $n_{d}^{1}$  with $\mathcal{L}_{left}^{rd}$ we obtain

@@

		\mathcal{L}_{left}^{rd}n_{d}^{1}&=\sum_{a,b=1}^{N}\alpha_{a}n_{b}^{x}\left((n_{d}^{1}-\bm{\delta}_{b}^{1}+\bm{\delta}_{a}^{1})-n_{d}^{1}\right)=\alpha_{d}\sum_{b=1\,:\,b\neq d}^{N}n_{b}^{1}-n_{d}^{1}\sum_{b=1\,:b\neq d}^{N}\alpha_{b}
		\alpha_{d}\left(\nu-n_{d}^{1}\right)-n_{d}^{1}\left(\nu(\sigma_{11}+(N-2)\sigma_{12})-\alpha_{d}\right)
		\\&=\alpha_{d}\nu-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})
		\nu\sigma_{11}\rho_{d}^{L}+\nu\sigma_{12}\left(\sum_{b=2\,:\,b\neq d}^{N}\rho_{b}^{1}\right)-n_{d}^{1}\nu(\sigma_{11}+(N-2)\sigma_{12})

@@

\subsubsection{Reversible measure for the reaction-diffusion process} 

@@

	\Lambda_{rev}=\bigtimes_{x=1}^{L}\Lambda_{rev}^{x}

@@

	\alpha_{a}=\beta_{a}\qquad\text{and}\qquad \alpha_{a}=\alpha_{b}=\alpha \quad \forall a,b\in \{1,\ldots,N-1\}

@@

	\rho=\rho_{a}=\frac{\alpha}{\alpha_{1}+(N-1)\alpha}\quad \forall a\in \{1,\ldots,N-1\}\qquad \text{and}\qquad \rho_{N}=\frac{\alpha_{1}}{\alpha_{1}+(N-1)\alpha}

@@

	\Lambda_{rev}^{x}(n^{x})=\frac{\nu!}{\prod_{a=1}^{N}n_{a}^{x}!}\rho^{\sum_{a=1}^{N-1}n_{a}^{x}}\rho_{1}^{n_{1}^{x}}
This can be proved just by imposing the detailed balance conditions for the edge $x,x+1$ and for the boundary generators. For fixed edge $x\in \{1,\ldots,L\}$ we only prove the detailed balance for  $\mathcal{L}_{x,x+1}^{c}$ with $c\in\{1,\ldots,N-2\}$ since for the other generators the computation is similar. Consider the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{g_{c}(b)}^{x}+\delta_{g_{c}(b)}^{x+1}-\delta_{b}^{x+1}$; the detailled balance reads
		&n_{a}^{x}n_{b}^{x+1}\frac{\nu!}{n_{1}^{x}!\cdots n_{a}^{x}!\cdots n_{g_{c}(b)}^{x}!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots n_{b}^{x+1}!\cdots n_{g_{c}(a)}^{x+1}!\ldots n_{N}^{x+1}!}\\&\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\cdots \rho_{a}^{n_{a}^{x}}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)}^{x+1}}

@@

		=&(n_{g_{c}(b)}^{x}+1)(n_{g_{c}(a)}^{x+1}+1)\frac{\nu!}{n_{1}^{x}!\cdots (n_{a}^{x}-1)!\cdots (n_{g_{c}(b)}^{x}+1)!\ldots n_{N}^{x}!}\frac{\nu!}{n_{1}^{x+1}!\cdots (n_{b}^{x+1}-1)!\cdots (n_{g_{c}(a)}^{x+1}+1)!\ldots n_{N}^{x+1}!}

@@

		\rho_{1}^{n_{1}^{x}+n_{1}^{x+1}}\ldots \rho_{a}^{n_{a}^{x}-1}\cdots\rho_{g_{c}(b)}^{n_{g_{c}(b)+1}^{x}}\cdots\rho_{b}^{n_{b}^{x+1}-1}\cdots \rho_{g_{c}(a)}^{n_{g_{c}(a)-1}^{x+1}}

@@

By similar computation it is possible to show that the same claim is obtained imposing the detailled balance for the transition $\bm{n}\to \bm{n}-\delta_{a}^{x}+\delta_{b}^{x}$, related to the generator $\mathcal{L}^{m}_{x,x+1}$. \\
For the boundary transitions we have that, analogously to what happens for the multispecies stirring process, the reservoirs parameters must be such that $\beta_{a}=\alpha_{a}$ and $\rho_{a}=\frac{\alpha_{a}}{|\alpha|}$. As a consequence we have the result. 
\subsubsection{Duality for the reaction-diffusion process}

@@

	\widetilde{\Omega}=\mathbb{N}_{0}^{N-1}\times  \bigtimes_{x\in V} \Omega_{x}\times \mathbb{N}_{0}^{N-1}
To sites $1,L$ we associate an ``extra site'', denoted by $0$ and $L+1$ respectively,

@@

	\bm{\xi}=\left(\xi_{2}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{2}^{L+1},\ldots,\xi_{N}^{L+1}\right)

@@

and the component $\xi_{a}^{0}$  gives the number of dual particles of type $a\in \{1,\ldots,N-1\}$ at 
the extra-site $0$ connected to $1$ and similarly for $xi_{a}^{L+1}$. \\

@@

	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{\xi_{a}^{u(x)}}\left(\prod_{x=1}^{L}\frac{(\nu -\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\right)\prod_{a=1}^{N-1}\left(\rho_{a}^{R}\right)^{\xi_{a}^{u(x)}}

@@

	\widetilde{\mathcal{L}}_{left}^{rd}=\widetilde{\mathcal{L}}^{rd}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{rd}+\widetilde{\mathcal{L}}_{right}^{rd}

@@

$\mathcal{L}_{x,x+1}^{rd}$ is defined in \eqref{edgeGeneratorRD} and, $\widetilde{\mathcal{L}}_{left}^{rd}$ and $\widetilde{\mathcal{L}}_{right}^{rd}$ are again the absorbing dual generators $\widetilde{\mathcal{L}}_{x}$ defined in \eqref{siteDualGenerator} and specialized for sites $x=1$ and $x=L$. 

@@

	H^{rd}=H_{left}+\sum_{x=1}^{L-1}\left(\sigma_{11}\mathcal{H}_{x,x+1}+\sigma_{12}\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}+(\Upsilon-2\sigma_{12})\mathcal{H}_{x,x+1}^{m}\right)+H_{right}
where $\mathcal{H}_{x,x+1}$ and $H_{left},H_{right}$ are \eqref{edgeHamiltonian}  and \eqref{siteHamiltonian} (with the choice of the boundary parameters done in \eqref{boundaryParamRD}) respectively, while
	\mathcal{H}_{x,x+1}^{c}=\sum_{a,b=0}^{N}\left(E_{g_{c}(a)b}\otimes E_{g_{c}(b)a}-E_{aa}\otimes E_{bb}\right)

@@

	\mathcal{H}_{x,x+1}^{m}=\sum_{a,b=1}^{N}\left(E_{ba}\otimes \mathbbm{1}-E_{aa}\otimes \mathbbm{1}\right)
Similarly, we will define the dual Hamiltonian $\widetilde{H}^{rd}$. For the edge dynamics, the original and the dual Hamiltonians do coincide, while the boundary ones are again $\widetilde{H}_{left},H_{right}$ defined in \eqref{siteDualHamiltonian}, but with the parameters introduced in \eqref{boundaryParamRD}.\\ We aim to show

@@

Therefore, we need to prove that, for arbitrary $x\in\{1,\ldots,L\}$
	(\mathcal{H}_{x,x+1}^{rd})^{T}D&=D\mathcal{H}_{x,x+1}^{rd}\label{edgeDualityRelationRD}\\
	H_{left}^{T}D&=D\widetilde{H}_{left}D\label{siteDualityRelationRD}
and similarly for $H_{right}$.
The duality matrix $D$ is again \eqref{dualityMatrix}. As already pointed out, $H_{left}$ and $\widetilde{H}_{left}$ have the same structure (up to a specific choice of the reservoirs parameters) therefore the duality relation for the boundaries is proved. However, $\mathcal{H}_{x,x+1}^{rd}$ has two more terms $\sum_{c=1}^{N-2}\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$. Therefore, we only need to show that 
	&(\mathcal{H}_{x,x+1}^{c})^{T}D=D\mathcal{H}_{x,x+1}^{c}\qquad \forall c\in \{1,\ldots,N-2\}\label{cDualityRelation}\\
	&(\mathcal{H}_{x,x+1}^{m})^{T}D=D\mathcal{H}_{x,x+1}^{m}\label{mDualityRelation}
